\Large \bf Dark Decoys: Conjuring Proxies from Unused Address Space

### 2019-02-14 paper/paper.tex
address entropy?

% to be able to draw some self-contained figs
\usepackage{tikz}
%\usepackage{parskip}
\usepackage{amsmath}
\usepackage{wasysym}
%\setlength{\parskip}{1pt} % 1ex plus 0.5ex minus 0.2ex}
\setlength\parskip{1pt}
\usepackage{graphicx} % http://ctan.org/pkg/graphicx
\usepackage{booktabs} % http://ctan.org/pkg/booktabs
\usepackage{xparse}   % http://ctan.org/pkg/xparse%don't print date
\NewDocumentCommand{\rot}{O{45} O{1em} m}{\makebox[#2][l]{\rotatebox{#1}{#3}}}%
\include{figures}
\usepackage{subcaption}
\usepackage{cleveref}

@@

>>>>

% to be able to draw some self-contained figs
\usepackage{tikz}
%\usepackage{parskip}
\usepackage{amsmath}
\usepackage{wasysym}
%\setlength{\parskip}{1pt} % 1ex plus 0.5ex minus 0.2ex}
\setlength\parskip{1pt}
\usepackage{graphicx} % http://ctan.org/pkg/graphicx
\usepackage{booktabs} % http://ctan.org/pkg/booktabs
\usepackage{xparse}   % http://ctan.org/pkg/xparse%don't print date
\NewDocumentCommand{\rot}{O{45} O{1em} m}{\makebox[#2][l]{\rotatebox{#1}{#3}}}%
\include{figures}
\usepackage{subcaption}
\usepackage{cleveref}
\usepackage{microtype}

% Slight JAH fix to stop URLs from breaking after ``http:''
\def\UrlBreaks{\do-\do\.\do\@\do\\\do\!\do\_\do\|\do\;\do\>\do\]%
 \do\)\do\,\do\?\do\'\do+\do\=\do\#}
\def\UrlBigBreaks{\do\:\do\/}%
\urlstyle{rm}

@@

\if0
\paragraph{Address entropy}
Addresses in IPv6 are commonly shortened, as many of the 128-bits in the address are set to 0.
For instance, google.com has the address
\texttt{2607:f8b0:400f:0806:0000:0000:0000:2004} (which can be shortened to
\texttt{2607:f8b0:400f:806::2004}). Only 24 bits are set to 1 in this address,
giving censors a possible feature to filter on: addresses that have too much
entropy could be suspicious as servers.
\fi
